### 2023-04-29 bachelorthesis/42-boxsizescan.tex
#39: Include paper, data, monitor code and status file in appendix, codestyle, chapter about methods, minor changes, flowdiagram style, new references
#39: Dedication, Acknowledgement, Abstract (ENG, DE), Eidstattliche Versicherung, Declaration

This chapter is an further iteration of the brief communication published in \enquote{Physics of Plasma}. It provides additional plots and paragraphs that were not necessary for the publication. the format was changed as well because the publication was written in REV\TeX~4.1 and this bachelor thesis in \texttt{scrreprt}. The brief communication can be found in the appendix of this thesis or under \textbf{REF PAPER GITHUB}.
%TODO

>>>>

%TODO
